\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{Software Engineer \hfill 08/2021 --- Present}}
\subtext{Patio \hfill Remote}
\vspace{3mm}
Built and maintained a react native application serving over two hundred thousand users, developing a responsive and scalable app, being responsible for the creation of multiple engineering docs, and architecting solutions. I was also responsible for developing some backend features using Node and Hasura and Firebase Cloud Functions.
\vspace{1mm}

% \begin{zitemize}
% \item Lorem ipsum dolor sit amet, consectetur adipiscing elit.
% \item Suspendisse pretium elit quis ullamcorper ultricies.
% \item Morbi a nisl sit amet massa ultricies fermentum.
% \item Sed a diam et turpis tempor venenatis eget eget ipsum.
% \item Vestibulum fermentum justo vitae aliquet accumsan.
% \end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Chapter Lead \hfill 01/2021 --- 08/2021}}
\subtext{Jungle Devs \hfill Florianópolis, Brazil}
\vspace{3mm}
As Hybrid Chapter Lead my main goal was promoting productive discussions towards innovation regarding Flutter and React Native and helping the development of other members of the team.
\vspace{1mm}

%====================
% EXPERIENCE C
%====================
\subsection{{Software Engineer \hfill 03/2020 --- 08/2021}}
\subtext{Jungle Devs \hfill Florianópolis, Brazil}
\vspace{3mm}
Worked as one of the lead react native developers, being responsible, among other things, for mentoring of two Junior Software Engineers, maintaining CI/CD of projects, and helping the company to grow by working on company OKRs and spreading the culture, being promoted multiple times.
\vspace{1mm}

%====================
% EXPERIENCE D
%====================
\subsection{{Software Engineer Intern \hfill 07/2019 --- 03/2020}}
\subtext{Jungle Devs \hfill Florianópolis, Brazil}
\vspace{3mm}
Worked in multiple React and React native projects shipping products for clients worldwide, maintaining FE AWS and Mobile deployment infrastructure in a couple of projects using terraform and Bitrise respectively. I was also responsible for an over 50\% decrease in build times for E2E testing.
\vspace{1mm}

%====================
% EXPERIENCE E
%====================
\subsection{{Front End Engineer Intern \hfill 11/2018 --- 07/2019}}
\subtext{PackIOT \hfill Florianópolis, Brazil}
\vspace{3mm}
As a Front End Engineer Intern I helped to develop products using React, Redux, HTML5, and CSS, working closely with designers and managers. I was also responsible for large performance improvements in the mobile web app, reducing load times and optimizing renders, in addition to that I also worked on backend tasks using Python and BigQuery.

%====================
% EXPERIENCE F
%====================
\subsection{{Web Developer Apprentice \hfill 08/2015 --- 07/2016}}
\subtext{Softplan \hfill Florianópolis, Brazil}
\vspace{3mm}
As a web developer apprentice in the marketing department, I had the opportunity to learn and work with PHP, SQL, HTML, JS, CSS and WordPress, creating and maintaining landing pages and developing internal systems using agile processes.


\end{document}
